---
title: "Developing Data Products - Course Project"
author: "Yash Jain"
date: "25th October 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
data(diamonds)
```

## Introduction

Have you ever wondered how diamonds are priced beyond the number of carats(or weight)? Price also depends on the diamond's cut, color, and clarity.

- Cut: quality of the diamond from best to worst (Ideal, Premium, Very Good, Good, Fair)
- Color: best(D) to worst(J)
- Clarity: measures how clear the diamond is from best to worst (IF, VVS2, VVS1, VS2, VS1, SI2, SI1, I1)

## Steps involved in the working of the App

This shiny app will predict diamond price based on your input of these factors.

- Essentially for a given input of cut, color and clarity all the data points corresponding to them are extracted from the data set "diamonds"
- Thereafter a model is trained with Price as output and Carat as input for the subsetted data. 
- Once the Model is trained user can give carat of diamond as input for which the predicted price will be displayed. A demonstration has been given in later slides.

## Documentation

Here is a summary of the "diamonds" dataset found in the ggplot2 R package. As you can see, the factors were measured in over 50,000 diamonds 
```{r,echo=TRUE,warning=FALSE,message=FALSE}
summary(diamonds[,c(1:4,7)])
```

## Summary plot of diamond data with each of the variables plotted against each other
```{r,echo=FALSE,warning=FALSE,message=FALSE }
plot(diamonds[,c(1:4,7)])
```

## A simple Demonstration of the App

- We subset data for cut = "Very Good", color = " F" and clarity = "IF".
```{r,echo=TRUE,message=FALSE,warning=FALSE, cache=TRUE}
diamond_subset <-subset(diamonds, cut == "Very Good" & color == "F" 
                        & clarity == "IF")
```

- We then train this sub-dataset for Price ~ Carat
```{r,echo=TRUE,warning=FALSE,message=FALSE,cache=TRUE}
fit <- lm(price~carat,data = diamond_subset)
```

- We next predict the price of diamond using the trained model for a carat value of 3.4
```{r,echo=TRUE,warning=FALSE,message=FALSE,cache=TRUE}
predict(fit,data.frame(carat=3.4))
```

## Links

The Shiny app and source code can be reached at:

- **shiny app**: https://yash-jain.shinyapps.io/Project_App/
- **source code**: https://github.com/yash7798/Developing-Data-Products-Course-Project


